\documentclass[]{article}

%\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{url}
%\pagestyle{fancy}
%\lhead{\footnotesize \parbox{11cm}{Mahmoud Zangeneh} }

\parindent=0pt
\usepackage[margin=0.5in]{geometry}

\begin{document}
\pagestyle{empty}
\begin{center}
{\large\textbf{Boyou Zhou}}\\
Department of Electrical and Computer Engineering, Boston University\\
8 St Mary's St, Photonics Center, Room 340, Boston, MA 02215\\
Email: bobzhou@bu.edu, Phone: 617-678-8480\\
\rule[-0.1cm]{7.5in}{0.01cm}
\end{center}
%

\textbf{Education}
\begin{table*}[h]
  %\newcommand{\z}{$^*$}
  %\centering
  \begin{tabular}{p{2.0in}p{2.0in}r}
    Boston University& Department of ECE & Ph.D. candidate, 2013 - present
    (GPA: 3.8/4.0)\\ 
    Southeast University & Department of ECE & B.S., 2013
    (Major GPA: 3.86/4.0)\\ 
  \end{tabular}
  \label{tbl:1}
\end{table*}

\noindent \textbf{Internship Experience}
    \begin{itemize}
        \item \textbf{Design Engineer at Analog Device Inc. San Jose, CA, June.2014-August.2014}\\
        Real Number Modeling ADP1048 PFC chip's application power stage with
        voltage-input-current-output feedback loop and chip's analog components, using Cadence
        Verilog-ams and verilog testbench for close loop simulation. Exploring the model with System
        Verilog to achieve consistency between \textit{Analog Device Inc.} Adice5 analog simulation
        and \textit{Cadence Incisive} digital simualtion. 
        \item \textbf{Design Engineer at Analog Device Inc. Wilmington, MA, June.2015-August.2015}\\
        Research on exploring Real Number Modeling using System Verilog. Set up environment for
        System Verilog Real Number Modeling, including Netlisting tool integration, netlisted code
        post-processing and data type library customization for RNM.
        \item \textbf{Job offered from \textit{Analog Device Inc.} as Design Engineer, July.2015}\\
        Position of firmware designer.
    \end{itemize}

\noindent \textbf{Research Experience, Oct.2013-May.2014, Sept.2014-Dec.2014}
%\textit{Accelerating Digital Logic Circuits Using Equalizers}
		\begin{itemize}
            \item Exploring the use of feedback equalization techniques to
            enhance the operating frequency of standard digital CMOS logic
            while consuming lower energy and mitigating timing errors. The
            proposed feedback equalizer lowers down the rise/fall time of
            the critical path based on the data sampled in the previous
            clock cycle. 

            \item Exploring equalization and bypassing techniques to mitigate
            the effects of transistor aging and post-fabrication
            variations in digital logic circuit designs.
		
        \end{itemize}

\noindent \textbf{Publication}
\begin{itemize}
    \item \textbf{Detecting hardware Trojans using backside optical imaging of
    embedded watermarks, \textit{2015 Design Automation Conference}}, first author
    
    Engineering a specific standard cell for photonic response Hardware Trojan Detection, comparing
    process variation using Monte Carlo simulation results with the timing and power analysis
    results from \textit{Cadence Encounter} ASIC Synthesis tool.

    \item \textbf{Rapid mapping of digital integrated circuit logic gates via multi-spectral backside
    imaging, \textit{2015 Optical Express}}

    Near-IR high resolution imaging and classifications for digital integrated circuits to detect
    Hardware Trojans.
\end{itemize}

\noindent \textbf{Relevant Courses}
\begin{itemize}
\item Graduate:
                    Hardware Security, Linux Kernel Programing in Embedded System, RF/IC Design,
                    Advanced Digital Design with Verilog and FPGA, Computer
                    Architecture, Digital VLSI Design, RF Analog VLSI Design,
                    Operating System, Hardware Security.
\item Undergraduate:
                    Digital Signal Processing, Communication System, Signals
                    and Systems, Computer Organization and 
                    Architecture, Electromagnetic Wave and Field. 
\end{itemize}

%CLASS PROJECTS AND UNDERGRADUATE PROJECTS
\noindent \textbf{Projects}
\begin{itemize}
    \item \textbf{Hardware Projects}
    \begin{itemize}
        \item \textbf{Digital:} 
        \begin{itemize}

            \item \verb+FPGA design+

            Designed an old fashioned game on Xilinx Spartan 6 with monitors and keyboard.  In particular,
            My design part involves the object movements, part of game logic and game AI using Verilog.


            \item \verb+CPU design+

            Design single CPU implemented on Spartan 6 FPGA that can execute 16 instructions and run
            basic assembly programs.

        \end{itemize}

        \item \textbf{Analog:} 

        \begin{itemize}

            \item \verb+1GHz-FM Receiver PCB design+

            Designed a demodulator down-converting from 1-GHz to baseband in order to achieve FM
            demodulation.

            \item \verb+RF/Analog VLSI design+ 

            Using cadence to design LNA, Gilbert Multiplier, Power Amplifier, Quadrature Oscillator and
            Phase Locked Loop at 5 GHz.

            \item \verb+Digital VLSI design+

            Compared 7T and 8T sub-threshold SRAM designs using Monte-Carlo Simulation.

        \end{itemize}

        \item \textbf{Mixed-Signal:}

        \begin{itemize}
            \item \verb+Metastability Driven True Random Number Generator+

            Using Cadence Virtuoso and Incisive to design TRNG using metastability of CMOS,
            configured by digital logic.
        \end{itemize}

    \end{itemize}

    \item \textbf{Firmware Projects}

    \begin{itemize}

        \item \verb+Embedded System Driver+

        Debug Bluetooth Communication Programming in Gumstix.

        \item \verb+Context Switch on Intel Machine and basic file system+

        Program Low level pre-emption on Intel Machine and basic file system in Operating System
        Course, running system on qemu.

    \end{itemize}

    \item \textbf{Software Projects}
        
    \begin{itemize} 

        \item \verb+Zombie Bird+

        Java game programming according to an online tutorial.

        \item \verb+CLRS pseudocodoe Translation+

        Translate all the algorithms in \textit{Introduction to Algorithms}, by Thomas H. Cormen,
        Charles E. Leiserson, Ronald L. Rivest, and Clifford Stein, into C++ codes, posted on
        \textit{Github}, working in progress.

        \item \verb+Color compilers+

        Color compiler output to the terminal, using Perl to intercept compiler process and re-post
        report in color on terminal.

        \item \verb+Mixed System Simulation Setup+
        
        Set up Ruby-driven Verilog, mixed system simulation, based cadence simulator and wave form
        viewer.

        \item Feel free to go to \url{http://github.com/byzhou}, and you will find more interesting
        projects I list here.

    \end{itemize} 
%\item Undergraduate Verilog design - 
%Designed and evaluated a multi-cycled 4004-processor having 20 instructions.

%\item Detection of Forbidden Electronics -
%Designed radio frequency bandpass filter using the Substrate Integrated
%Waveguide with HFSS.

%\item GPS/BeiDou/RFID Continuous Positioning Systems based on embedded system -
%Set up the communication modules between the GPS and the central processor.

\end{itemize}

\noindent \textbf{Skills}
\begin{itemize}
\item Programming Languages:  Verilog/Verilog-ams/System Verilog, Perl, Python, C, C++, Ruby, Bash,
Hspice, Adice5, Java, markdown
\item Softwares: git/git-svn, vim, gcc/g++, qemu, gdb, emacs, Matlab, Makefile, Lingo, latex/latexmk, eclipse
\item Circuit Design Tools:  incisive, simvision, Modelsim, Altium Designer, Cadence
rc$\&$encounter, HSPICE, Cadence Virtuoso, Virtuoso Layout Editor, LabView, Xilinx ISE, Quartus II,
HFSS, Microwave Office. 

\end{itemize}
%\newpage
\noindent \textbf{Awards}
\begin{itemize}
\item 09/2013:  ECE fellowship, Boston University.

\item 03/2012:  Honorable Prize in Interdisciplinary Competition of Modeling
(Competition Organized by COMAP, the Consortium for Mathematics and Its
Applications).

%\item 09/2011:  First Class Prize in Mathematics Competition of Modeling in
%Jiangsu Province (Competition Organized by Jiangsu Society for Industrial and
%Applied Mathematics).

%\item 07/2010:  Second Class Prize of Mathematics Competition in Jiangsu
%Province (Competition Organized by Department of Higher Education of Ministry
%of Education and China Society for Industrial and Applied Mathematics).

\end{itemize}

\noindent \textbf{Teaching Experience}
\begin{itemize}
\item Graduate Teaching Fellow for Operating System (Raspberry pi working platform) at Boston
University
(Spring 2014).
\item Graduate Teaching Fellow for Introduction to Software Engineering (C++) (Fall
2013).
\end{itemize}

\end{document}
